P.berghei pir analysis

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
save biplot

plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005),
             inherit.aes = FALSE, size = 0.75) +
  geom_label_repel(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005,
                 label = Geneid),
             inherit.aes = FALSE, size = 3,
            nudge_x = 0.4,
            force = 100)
```

>>>>

loadings_scale <- 0.005

bp <- plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*loadings_scale, y = PC2*loadings_scale),
             inherit.aes = FALSE, size = 0.75) +
  geom_label_repel(data = pca_object_loadings,
             aes(x = PC1*loadings_scale, y = PC2*loadings_scale,
                 label = Geneid),
             inherit.aes = FALSE, size = 3,
            nudge_x = 0.4,
            force = 100)

ggsave('thesis_chapter3_figure_biplot.png',
       bp)
